---
title: "Mission EDA"
author: "Stockton Nelson"
format: pdf
editor: visual
---

## Setup

```{r}
#Downloading Libraries
library(tidyverse)     #Standard R Functions
library(tidytext)      #TF-IDF Analysis
library(patchwork)     #Plotting multiple plots together
library(flextable)     #Making Presentable Tables
library(stringr)       #Formatting Text Data
library(purrr)         #Formatting Text Data

#Bringing in Data
mission <- readxl::read_excel("Missionary_Memorabilia.xlsx", skip = 1) |>
  janitor::clean_names()
```

## Data Wrangling

```{r}
#Obtaining Columns Names
qn <- vector("character", length = 15)
for (i in 19:33){
  qn[i-18] <- colnames(mission)[i]
}
```

```{r}
#Renaming and Filtering Missing Data
mission_missing <- mission |>
  rename(Q1 = qn[1], Q2 = qn[2], Q3 = qn[3], Q4 = qn[4], Q5A = qn[5],
         Q5B = qn[6], Q5C = qn[7], Q5D = qn[8], Q5E = qn[9], Q5F = qn[10],
         Q5G = qn[11], Q5H = qn[12], Q5 = qn[13], Q6 = qn[14], Q7 = qn[15],
         duration = duration_in_seconds, latitude = location_latitude,
         longitude = location_longitude, recaptcha = q_recaptcha_score) |>
  dplyr::select(-recipient_last_name, -recipient_first_name,
                -recipient_email, -external_data_reference) |>
  filter((is.na(Q4) & is.na(Q6)) | is.na(Q3))
```

```{r}
#Renaming and Filtering Usable Data
mission <- mission |>
  rename(Q1 = qn[1], Q2 = qn[2], Q3 = qn[3], Q4 = qn[4], Q5A = qn[5],
         Q5B = qn[6], Q5C = qn[7], Q5D = qn[8], Q5E = qn[9], Q5F = qn[10],
         Q5G = qn[11], Q5H = qn[12], Q5 = qn[13], Q6 = qn[14], Q7 = qn[15],
         duration = duration_in_seconds, latitude = location_latitude,
         longitude = location_longitude, recaptcha = q_recaptcha_score) |>
  dplyr::select(-recipient_last_name, -recipient_first_name,
         -recipient_email, -external_data_reference) |>
  filter((!is.na(Q4) | !is.na(Q6)) & !is.na(Q3))
```

## Exploratory Data Analysis

### Geographic Makeup

```{r}
#Getting World Map Data
world <- rnaturalearth::ne_countries(scale = "medium", returnclass = "sf")

#Plotting the World Map of Survey Data
ggplot() +
  geom_sf(data = world, fill = "gray90", color = "black") +
  geom_point(data = mission, aes(x = longitude, y = latitude),
             color = "#FF2E00", fill = "#FF2E00", alpha = 0.5, size = 1.5) +
  coord_sf() +
  labs(x = "Longitude", y = "Latitude", title = "Survey Data World Map",
       subtitle = "Where each missionary took the survey") +
  theme_minimal() +
  theme(panel.border = element_rect(color = "black", fill = NA, linewidth = 1),
        panel.background = element_rect(fill = "#D4E4ED", color = NA))

#Saving Plot
# ggsave(
#   filename = "World_Geography.png",
#   plot = last_plot(),
#   width = 10,
#   height = 6,
#   dpi = 300
# )
```

```{r}
#Getting the US Map
mission_us <- mission |>
  filter(
    longitude >= -125 & longitude <= -66 &
    latitude >= 24 & latitude <= 49
  ) |> 
  filter(
    !(longitude > -80 & latitude > 43)
  )

#Plotting the US Map of Survey Data
us_states <- map_data("state")
ggplot() +
  geom_polygon(data = us_states, aes(x = long, y = lat, group = group),
               fill = "gray90", color = "black") +
  geom_point(data = mission_us, aes(x = longitude, y = latitude), 
             color = "#FF2E00", alpha = 0.5) +
  labs(x = "Longitude", y = "Latitude", title = "Survey Data US Map",
       subtitle = "Where each missionary took the survey") +
  theme_minimal() +
  theme(panel.border = element_rect(color = "black", fill = NA, linewidth = 1),
        panel.background = element_rect(fill = "#D4E4ED", color = NA))

#Saving Plot
# ggsave(
#   filename = "US_Geography.png",
#   plot = last_plot(),
#   width = 10,
#   height = 6,
#   dpi = 300
# )
```

**Conclusion:** 1,308 responses, all with valid coordinates, zero at (0,0) — no failed lookups. 1,220 North America / 87 international / 1 Latin America by IP address. 249 served in Latin America, but 246 of them now have a North American IP — i.e., home, not misplaced. The international IPs resolve to real LDS cities (Kinshasa, Abidjan, Accra…), and the only non-English text is French from that francophone-Africa group (18 respondents, zero Spanish) — proof the geolocation correctly separates domestic from abroad.

### Demographic Analysis

```{r}
#Cleaning up Mission Regions
collapse_region <- function(x) {
  dplyr::case_when(
    is.na(x) | x == ""              ~ "Unknown",
    str_detect(x, ",")     ~ "Multiple Regions",
    TRUE                            ~ x
  )
}

#Making Dataset for Demographics Table
mission_table <- mission |>
  dplyr::mutate(q1_region = collapse_region(q1_region)) |>
  select(q1_region, Q2, Q3, Q6) |>
  rename(Q1 = q1_region) |>
  mutate(across(c(Q2, Q3, Q6), as.character)) |>
  mutate(Q6 = ifelse(is.na(Q6), "Unknown", Q6)) |>
  mutate(Q3 = ifelse(Q3 == "6 - 12 months", "6-12 months", Q3)) |>
  rename(`Mission Region` = Q1,
          Missionary = Q2,
         `Time Since Mission` = Q3,
         `Memorabilia Importance` = Q6)

mission_table <- mission_table |>
  mutate(
    `Mission Region` = factor(`Mission Region`,
                              levels = c("U.S./Canada", "Europe", 
                                         "South America", "Africa",
                                         "Asia", "Central America",
                                         "Oceania", "Multiple Regions",
                                         "Unknown")),
    `Time Since Mission` = factor(`Time Since Mission`,
                                  levels = c("Less than 6 months",
                                             "6-12 months",
                                             "1-3 years","3-5 years",
                                             "5-10 years","10-20 years",
                                             "20-30 years","30-40 years",
                                             "40+ years")),
    `Memorabilia Importance` = factor(`Memorabilia Importance`,
                                      levels = c("Not at all important",
                                                 "Slightly important",
                                                 "Moderately important",
                                                 "Very important",
                                                 "Extremely important",
                                                 "Unknown")))

#Making Demographic Table
demo_table <- table1::table1(~ `Mission Region` + Missionary + 
                               `Time Since Mission` + `Memorabilia Importance`, 
                             data = mission_table) |>
  table1::t1flex() |>
  theme_zebra()

#Exporting Demographic Table
# gg <- gen_grob(demo_table, fit = "auto")
# ggplot2::ggsave("demographics_table.pdf", plot = gg,
#                 width = 4, height = 8, units = "in")
```

```{r}
#Cleaning up Mission Regions
collapse_region <- function(x) {
  dplyr::case_when(
    is.na(x) | x == ""              ~ "Unknown",
    str_detect(x, ",")     ~ "Multiple Regions",
    TRUE                            ~ x
  )
}

#Making Dataset for Demographics Table
mission_table <- mission |>
  dplyr::mutate(q1_region = collapse_region(q1_region)) |>
  select(q1_region, Q2, Q3, Q6) |>
  rename(Q1 = q1_region) |>
  mutate(across(c(Q2, Q3, Q6), as.character)) |>
  mutate(Q2 = ifelse(is.na(Q2), "Unknown", Q2),
         Q3 = ifelse(is.na(Q3), "Unknown", Q3),
         Q6 = ifelse(is.na(Q6), "Unknown", Q6)) |>
  mutate(Q3 = ifelse(Q3 == "6 - 12 months", "6-12 months", Q3)) |>
  rename(`Mission Region` = Q1,
         Missionary = Q2,
         `Time Since Mission` = Q3,
         `Memorabilia Importance` = Q6)

mission_table <- mission_table |>
  mutate(
    `Mission Region` = factor(`Mission Region`,
                              levels = c("U.S./Canada", "Europe", 
                                         "South America", "Africa",
                                         "Asia", "Central America",
                                         "Oceania", "Multiple Regions",
                                         "Unknown")),
    `Time Since Mission` = factor(`Time Since Mission`,
                                  levels = c("Less than 6 months",
                                             "6-12 months",
                                             "1-3 years","3-5 years",
                                             "5-10 years","10-20 years",
                                             "20-30 years","30-40 years",
                                             "40+ years","Unknown")),
    `Memorabilia Importance` = factor(`Memorabilia Importance`,
                                      levels = c("Not at all important",
                                                 "Slightly important",
                                                 "Moderately important",
                                                 "Very important",
                                                 "Extremely important",
                                                 "Unknown")))

#Making Demographic Table
demo_table <- table1::table1(~ `Mission Region` + Missionary + 
                               `Time Since Mission` + `Memorabilia Importance`, 
                             data = mission_table) |>
  table1::t1flex() |>
  theme_zebra()

#Exporting Demographic Table
gg <- gen_grob(demo_table, fit = "auto")
ggplot2::ggsave("demographics_table.pdf", plot = gg,
                width = 4, height = 8, units = "in")
```

### Question 1

```{r}
#Getting Word Counts
Q1_region_counts <- mission |>
  tidyr::separate_longer_delim(q1_region, delim = regex(",\\s*")) |>
  dplyr::filter(!is.na(q1_region), q1_region != "") |>
  dplyr::count(q1_region, sort = TRUE) |>
  mutate(pct = n / sum(n),
         label = paste0(n, " (", scales::percent(pct, accuracy = 1), ")"))
```

```{r}
#Making Bar Chart of Mission Regions
ggplot(Q1_region_counts, aes(x = reorder(q1_region, n), y = n)) +
  geom_col(fill = "#566246") +
  geom_text(aes(label = label), y = Inf, hjust = -0.1) +
  coord_flip(clip = "off") +
  labs(
    title = "Missionary Service by Region",
    x = "",
    y = "Count"
  ) +
  theme(plot.margin = margin(t = 10, r = 60, b = 10, l = 0))

#Saving Plot
# ggsave(
#   filename = "Mission_Regions.png",
#   plot = last_plot(),
#   width = 10,
#   height = 6,
#   dpi = 300
# )
```

```{r}
#Getting Missions
Q1_mission_counts <- mission |>
  filter(!is.na(q1_cleaned), q1_cleaned != "") |>
  tidyr::separate_longer_delim(q1_cleaned, delim = regex("\\s*,\\s*")) |>
  mutate(q1_cleaned = str_trim(q1_cleaned)) |>
  filter(q1_cleaned != "") |>
  count(q1_cleaned, sort = TRUE, name = "n")
```

```{r}
#Making Bar Chart of Word Counts
Q1_mission_counts |>
  slice_max(n, n = 20) |>
  ggplot(aes(x = reorder(q1_cleaned, n), y = n)) +
  geom_col(fill = "#879970") +
  geom_text(aes(label = n), y = Inf, hjust = -0.1) +
  coord_flip(clip = "off") +
  labs(
    title = "Top 20 Most Common Missions",
    x = "",
    y = "Count"
  ) +
  theme(plot.margin = margin(t = 10, r = 30, b = 10, l = 0))

#Saving Plot
# ggsave(
#   filename = "Missions.png",
#   plot = last_plot(),
#   width = 10,
#   height = 6,
#   dpi = 300
# )
```

```{r}
#Getting Cumulative Percentage
grand_total <- sum(Q1_mission_counts$n)
pareto_data <- Q1_mission_counts |>
  arrange(desc(n)) |>
  slice_head(n = 10) |>
  mutate(
    mission = factor(q1_cleaned, levels = q1_cleaned),
    cum_pct = cumsum(n) / grand_total
  )
scale_factor <- max(pareto_data$n)

#Making Pareto Chart of Missions
ggplot(pareto_data, aes(x = mission)) +
  geom_col(aes(y = n), fill = "#6E7B57") +
  geom_text(aes(label = n), y = Inf, vjust = -0.5) +
  geom_line(aes(y = cum_pct * scale_factor, group = 1)) +
  geom_point(aes(y = cum_pct * scale_factor)) +
  scale_y_continuous(
    name = "Count",
    expand = expansion(mult = c(0, 0.1)),
    sec.axis = sec_axis(~ . / scale_factor, labels = scales::percent,
                        name = "Cumulative %")
  ) +
  labs(x = "Mission", title = "Pareto Chart: Top 10 Missions") +
  coord_cartesian(clip = "off") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        plot.title = element_text(margin = margin(b = 20)),
        plot.margin = margin(t = 10, r = 10, b = 10, l = 10))

#Saving Plot
# ggsave(
#   filename = "Pareto_Missions.png",
#   plot = last_plot(),
#   width = 10,
#   height = 6,
#   dpi = 300
# )
```

```{r}
#Getting Table of Number of People for Each Mission
ftm <- Q1_mission_counts |>
  count(n, name = "Number of Missions") |>
  arrange(n) |>
  rename("Number of Missionaries" = n) |>
  flextable() |>
  theme_booktabs() |>
  bold(part = "header") |>
  align(align = "center", part = "all") |>
  add_footer_lines(paste0("Total Number of Missions: ", 
                          nrow(Q1_mission_counts))) |>
  bold(part = "footer") |>
  autofit() |>
  bg(bg = "white", part = "all")

#Saving Table
# save_as_image(ftm, path = "cross_table_Mission_Counts.png")
```

### Question 2

```{r}
#Getting Words
Q2 <- mission |>
  unnest_tokens(word, Q2)

#Getting Word Counts
Q2_word_counts <- Q2 |>
  filter(!is.na(word)) |>
  count(word, sort = TRUE) |>
  mutate(pct = n / sum(n),
         label = paste0(n, " (", scales::percent(pct, accuracy = 1), ")")) |>
  mutate(word = case_when(
    word == "elder" ~ "Elder",
    word == "sister" ~ "Sister",
    TRUE ~ word
  ))
```

```{r}
#Making Bar Chart of Word Counts
Q2_word_counts |>
  ggplot(aes(x = reorder(word, n, na.rm = TRUE), y = n, fill = word)) +
  geom_col() +
  geom_text(aes(label = label), y = Inf, hjust = -0.1) +
  coord_flip(clip = "off") +
  scale_fill_manual(values = c(
    "Elder" = "#2986cc",
    "Sister" = "#c90076"
  )) +
  labs(
    title = "Elder vs Sister Missionaries",
    x = "",
    y = "Count"
  ) +
  theme(legend.position = "none",
        plot.margin = margin(t = 10, r = 60, b = 10, l = 0))

#Saving Plot
# ggsave(
#   filename = "Elders_Sisters.png",
#   plot = last_plot(),
#   width = 10,
#   height = 6,
#   dpi = 300
# )
```

### Question 3

```{r}
#Gathering the Time Levels
time_levels <- c(
  "Less than 6 months",
  "6 - 12 months",
  "1-3 years",
  "3-5 years",
  "5-10 years",
  "10-20 years",
  "20-30 years",
  "30-40 years",
  "40+ years"
)

#Making Data for Question 3 Counts
Q3 <- mission |> 
  filter(!is.na(Q3)) |>
  mutate(time_range = factor(Q3, levels = time_levels)) |>
  mutate(order_index = as.numeric(time_range)) 

#Making Data for Question 3 Percentages
Q3_counts <- Q3 |>
  count(time_range) |>
  mutate(pct = n / sum(n),
         label = paste0(n, " (", scales::percent(pct, accuracy = 1), ")")) |>
  mutate(time_range = factor(time_range, levels = rev(time_levels))) |>
  mutate(order_index = as.numeric(factor(time_range, levels = time_levels)))
```

```{r}
#Making Bar Chart of Word Counts
ggplot(Q3_counts, aes(x = time_range, y = n, fill = order_index)) +
  geom_col() +
  geom_text(aes(label = label), y = Inf, hjust = -0.1) +
  coord_flip(clip = "off") +
  scale_fill_gradient(low = "#8B0000", high = "#FFCCCC") +
  labs(title = "Time Since Missionary Service", 
       x = "", 
       y = "Count") +
  theme(legend.position = "none",
        plot.margin = margin(t = 10, r = 60, b = 10, l = 0))

#Saving Plot
# ggsave(
#   filename = "Time_Since_Service.png",
#   plot = last_plot(),
#   width = 10,
#   height = 6,
#   dpi = 300
# )
```

### Question 4

```{r}
#Reformatting Q4 Answers
mission_long <- mission |>
  mutate(Q4 = gsub("Other", "From Other", Q4)) |>
  separate_rows(Q4, sep = ",(?=From)") |>
  mutate(Q4 = trimws(Q4))

#Categorizing Q4 Answers
Q4 <- mission_long |>
  mutate(item_source = case_when(
    grepl("Church", Q4) ~ "Church",
    grepl("mission leaders", Q4) ~ "Mission Leaders",
    grepl("home ward", Q4) ~ "Ward/Stake",
    grepl("members|converts|friends", Q4) ~ "Members/Friends",
    grepl("fellow missionaries", Q4) ~ "Fellow Missionaries",
    grepl("parents|family", Q4) ~ "Family",
    grepl("personal records", Q4) ~ "Personal Records",
    grepl("Other", Q4) ~ "Other",
    TRUE ~ NA_character_
  ))

#Finding Counts and Percentage
total_respondents <- mission |>
  filter(!is.na(Q4)) |>
  nrow()
Q4_word_counts <- Q4 |>
  count(item_source) |>
  filter(!is.na(item_source)) |>
  arrange(desc(n)) |>
  mutate(pct = n/total_respondents,
         label = scales::percent(pct, accuracy = 1),
         label = paste0(scales::percent(pct, accuracy = 1), " (", n, ")"))
```

```{r}
#Making Bar Chart of Word Counts
Q4_word_counts |>
  ggplot(aes(x = reorder(item_source, n), y = pct)) +
  geom_col(fill = "#DA9D19") +
  geom_text(aes(label = label), y = Inf, hjust = -0.1) +
  scale_y_continuous(labels = scales::percent,
                     breaks = seq(0, 1, by = 0.1)) +
  coord_flip(clip = "off") +
  labs(
    title = "Sources of Missionary Memorabilia",
    x = "Source",
    y = "Percentage"
  ) +
  theme(plot.margin = margin(t = 10, r = 65, b = 10, l = 10))

#Saving Plot
# ggsave(
#   filename = "Memorabilia_Sources.png",
#   plot = last_plot(),
#   width = 10,
#   height = 6,
#   dpi = 300
# )
```

### Question 5

See Modeling Section.

### Question 6

```{r}
#Gathering the Importance Levels
importance_levels <- c(
  "Not at all important",
  "Slightly important",
  "Moderately important",
  "Very important",
  "Extremely important"
)

#Making Data for Question 6 Counts
Q6 <- mission |> 
  filter(!is.na(Q6)) |>
  mutate(importance = factor(Q6, levels = importance_levels)) |>
  mutate(order_index = as.numeric(importance))

#Making Data for Question 3 Percentages
Q6_counts <- Q6 |>
  count(importance) |>
  mutate(pct = n / sum(n),
         label = paste0(n, " (", scales::percent(pct, accuracy = 1), ")")) |>
  mutate(importance = factor(importance, levels = importance_levels)) |>
  mutate(order_index = as.numeric(factor(importance, levels = importance_levels)))
```

```{r}
#Making Bar Chart of Word Counts
ggplot(Q6_counts, aes(x = importance, y = n, fill = order_index)) +
  geom_col() +
  geom_text(aes(label = label), y = Inf, hjust = -0.1) +
  coord_flip(clip = "off") +
  scale_fill_gradient(low = "#B7C0CC", high = "#3B4554") +
  labs(title = "Importance of Missionary Memorabilia", 
       x = "", 
       y = "Count") +
  theme(legend.position = "none",
        plot.margin = margin(t = 10, r = 60, b = 10, l = 0))

#Saving Plot
# ggsave(
#   filename = "Memorabilia_Importance.png",
#   plot = last_plot(),
#   width = 10,
#   height = 6,
#   dpi = 300
# )
```

### Question 7

```{r}
#Getting Words
Q7 <- mission |>
  filter(!is.na(Q7)) |>
  unnest_tokens(word, Q7)

#Getting Word Counts
Q7_word_counts <- Q7 |>
  count(word, sort = TRUE) |>
  anti_join(stop_words, by = "word") 

#Making Bar Chart of Word Counts
Q7_word_counts |>
  slice_max(n, n = 15) |>
  ggplot(aes(x = reorder(word, n), y = n)) +
  geom_col(fill = "#79A9D1") +
  geom_text(aes(label = n, y = max(n) * 1.02), hjust = 0) +
  scale_y_continuous(expand = expansion(mult = c(0, 0.09))) +
  coord_flip() +
  labs(
    title = "Top 15 Most Common Words in Question 7",
    x = "Word",
    y = "Count"
  )
```

### Questions 3 & 6

```{r}
#Cross Table of Time and Memorabilia Importance
ftti <- mission |>
  mutate(Q3_grouped = case_when(
    Q3 %in% c("Less than 6 months", "6 - 12 months") ~ "<1 yr",
    Q3 %in% c("1-3 years", "3-5 years")              ~ "1-5 yr",
    Q3 %in% c("5-10 years", "10-20 years")           ~ "5-20 yr",
    Q3 %in% c("20-30 years", "30-40 years", "40+ years") ~ "20+ yr"
  )) |>
  mutate(Q3_grouped = factor(Q3_grouped, levels = c("<1 yr", "1-5 yr",
                                                    "5-20 yr", "20+ yr")),
         Q6 = factor(Q6, levels = importance_levels)) |>
  rename(`Time from Missionary Service` = Q3_grouped) |>
  janitor::tabyl(`Time from Missionary Service`, Q6, show_na = FALSE) |>
  janitor::adorn_totals(c("row", "col")) |>
  janitor::adorn_percentages("row") |>
  janitor::adorn_pct_formatting(digits = 1) |>
  janitor::adorn_ns() |>
  flextable() |>
  autofit() |>
  bg(bg = "white", part = "all")

#Saving Table
# save_as_image(ftti, path = "cross_table_TSS_Importance.png")
```

```{r}
#Making the Data for the Plot
bar_chart36 <- mission |>
  filter(!is.na(Q6), !is.na(Q3)) |>
  mutate(Q3_grouped = case_when(
    Q3 %in% c("Less than 6 months", "6 - 12 months") ~ "<1 yr",
    Q3 %in% c("1-3 years", "3-5 years")              ~ "1-5 yr",
    Q3 %in% c("5-10 years", "10-20 years")           ~ "5-20 yr",
    Q3 %in% c("20-30 years", "30-40 years", "40+ years") ~ "20+ yr"
  )) |>
  mutate(Q3_grouped = factor(Q3_grouped, levels = c("<1 yr", "1-5 yr",
                                                    "5-20 yr", "20+ yr")),
         Q6 = factor(Q6, levels = importance_levels)) |>
  count(Q3_grouped, Q6, .drop = FALSE) |>
  group_by(Q3_grouped) |>
  mutate(pct = n / sum(n)) |>
  ungroup()

#Making the Side by Side Bar Charts
ggplot(bar_chart36, aes(x = Q3_grouped, y = pct, fill = Q6)) +
  geom_col(position = "dodge") +
  scale_x_discrete(labels = c(
    "<1 yr"   = "<1 yr\n(n=200)",
    "1-5 yr"  = "1-5 yr\n(n=347)",
    "5-20 yr" = "5-20 yr\n(n=239)",
    "20+ yr"  = "20+ yr\n(n=245)"
  )) +
  scale_y_continuous(labels = scales::percent) +
  scale_fill_manual(labels = c(
    "Not at all important" = "None",
    "Slightly important"   = "Slightly",
    "Moderately important" = "Moderately",
    "Very important"       = "Very",
    "Extremely important"  = "Extremely"
  ), values = colorRampPalette(c("#B7C0CC", "#3B4554"))(5)) +
  labs(x = "Time from Missionary Service",
       y = "Percentage",
       fill = "Importance",
       title = "Memorabilia Importance by Time Since Missionary Service")

#Saving Plot
# ggsave(
#   filename = "Importance_TSS.png",
#   plot = last_plot(),
#   width = 10,
#   height = 6,
#   dpi = 300
# )
```

```{r}
#Making the Data for the Plot
bar_chart63 <- mission |>
  filter(!is.na(Q6), !is.na(Q3)) |>
  mutate(Q3_grouped = case_when(
    Q3 %in% c("Less than 6 months", "6 - 12 months") ~ "<1 yr",
    Q3 %in% c("1-3 years", "3-5 years")              ~ "1-5 yr",
    Q3 %in% c("5-10 years", "10-20 years")           ~ "5-20 yr",
    Q3 %in% c("20-30 years", "30-40 years", "40+ years") ~ "20+ yr"
  )) |>
  mutate(Q3_grouped = factor(Q3_grouped, levels = c("<1 yr", "1-5 yr",
                                                    "5-20 yr", "20+ yr")),
         Q6 = factor(Q6, levels = importance_levels)) |>
  count(Q3_grouped, Q6, .drop = FALSE) |>
  group_by(Q6) |>
  mutate(pct = n / sum(n)) |>
  ungroup()

#Making the Side by Side Bar Charts
ggplot(bar_chart63, aes(x = Q6, y = pct, fill = Q3_grouped)) +
  geom_col(position = "dodge") +
  scale_x_discrete(labels = c(
    "Not at all important" = "None\n(n=14)",
    "Slightly important"   = "Slightly\n(n=84)",
    "Moderately important" = "Moderately\n(n=189)",
    "Very important"       = "Very\n(n=366)",
    "Extremely important"  = "Extremely\n(n=378)"
  )) +
  scale_y_continuous(labels = scales::percent) +
  scale_fill_manual(values = colorRampPalette(c("#8B0000", "#FFCCCC"))(4)) +
  labs(x = "Importance",
       y = "Percentage",
       fill = "Time from Service",
       title = "Time Since Missionary Service by Memorabilia Importance")

#Saving Plot
# ggsave(
#   filename = "TSS_Importance.png",
#   plot = last_plot(),
#   width = 10,
#   height = 6,
#   dpi = 300
# )
```

```{r}
#Making the Data for the Plot
line_plot <- mission |>
  filter(!is.na(Q6), !is.na(Q3)) |>
  mutate(Q3_grouped = case_when(
    Q3 %in% c("Less than 6 months", "6 - 12 months") ~ "Less than a year",
    Q3 %in% c("1-3 years", "3-5 years")              ~ "1-5 years",
    Q3 %in% c("5-10 years", "10-20 years")           ~ "5-20 years",
    Q3 %in% c("20-30 years", "30-40 years", "40+ years") ~ "20+ years"
  )) |>
  count(Q3_grouped, Q6) |>
  group_by(Q3_grouped) |>
  mutate(pct = n / sum(n),
         Q3_grouped = factor(Q3_grouped, levels = c("Less than a year", 
                                                    "1-5 years",
                                                    "5-20 years",
                                                    "20+ years")),
         Q6 = factor(Q6, levels = importance_levels)) |>
  ungroup()

#Making Line Plot of Memorabilia Importance and Time from Service
ggplot(line_plot, aes(x = Q6, y = pct, group = Q3_grouped, 
                         color = Q3_grouped)) +
  geom_line(linewidth = 1.125) +
  scale_x_discrete(labels = c(
    "Not at all important" = "None",
    "Slightly important"   = "Slightly",
    "Moderately important" = "Moderately",
    "Very important"       = "Very",
    "Extremely important"  = "Extremely"
  )) +
  scale_y_continuous(labels = scales::percent) +
  scale_color_manual(values = colorRampPalette(c("#8a081f", "#f2a7a7"))(4)) +
  labs(x = "Memorabilia Importance",
       y = "Percentage",
       color = "Time since Mission", 
       title = "Memorabilia Importance by Time since Mission")

#Saving Plot
# ggsave(
#   filename = "TSS_Importance_Trend.png",
#   plot = last_plot(),
#   width = 10,
#   height = 6,
#   dpi = 300
# )
```

```{r}
#Making Table for Chi-Squared Test
tab <- mission |>
  filter(!is.na(Q6), !is.na(Q3)) |>
  mutate(
    Q3 = ifelse(Q3 == "6 - 12 months", "6-12 months", Q3),
    Q3_grouped = case_when(
      Q3 %in% c("Less than 6 months", "6-12 months")     ~ "Less than a year",
      Q3 %in% c("1-3 years", "3-5 years")                ~ "1-5 years",
      Q3 %in% c("5-10 years", "10-20 years")             ~ "5-20 years",
      Q3 %in% c("20-30 years", "30-40 years", "40+ years") ~ "20+ years"),
    Q3_grouped = factor(Q3_grouped,
                        levels = c("Less than a year", "1-5 years", 
                                   "5-20 years", "20+ years")),
    Q6 = factor(Q6, levels = importance_levels)) |>
  with(table(Q3_grouped, Q6))

#Running Chi-Squared Test
set.seed(12)
chisq.test(tab, simulate.p.value = TRUE, B = 10000)
```

### Other

```{r}
#Chaning Time Order
mission_missing <- mission_missing |>
  mutate(Q3 = factor(Q3, levels = c("Less than 6 months",
                                    "6 - 12 months",
                                    "1-3 years",
                                    "3-5 years",
                                    "5-10 years",
                                    "10-20 years",
                                    "20-30 years",
                                    "30-40 years",
                                    "40+ years")))

#Making Plot of Missing Time Responses
ggplot(mission_missing, aes(x = Q3)) +
  geom_bar(fill = "#F8333C") +
  geom_text(stat = "count",
            aes(label = after_stat(count)),
            y = Inf, hjust = -0.1) +
  coord_flip(clip = "off") +
  scale_x_discrete(limits = rev) +
  labs(x = "Time Since Service",
       y = "Count",
       title = "Missing Data Distribution") +
  theme(plot.margin = margin(t = 10, r = 20, b = 10, l = 0))

#Saving Plot
# ggsave(
#   filename = "Missing_Time.png",
#   plot = last_plot(),
#   width = 10,
#   height = 6,
#   dpi = 300
# )
```
